---
title: "ophcitation-analysis01-penalizedregression"
author: "Sophia Wang"
date: "July 13, 2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data Cleanup 
```{r}
library(tidyverse)
```


```{r}
df <- read.csv('dfscopus-2.csv')
```
Note to self. Do not try to doubleclick on the df and open it in R (takes forever to load)

Remove variables we won't use or those that are redundant 
```{r}
df <-select(df, -index, -authorlist, -authoridlist, -access.type)
```

filter out missing values in tc - turns out there;s 2196 rows of missing values 
Create Boolean TC varaible 
```{r}
df<-filter(df, !is.na(tc))
```

```{r}
quantile(df$tc, c(0.75))
```
```{r}
df$tcB<-ifelse(df$tc>=20, 1, 0)
```


Check what other columns have missing values - these are going to give us problems in the glmnet 
Turns out that many of the ik_ and ak_ columns have missing values, I wonder why? 
I'm going to fill na pagecount with 1 (presume one page)
then fill na the others with 0 (presume those keywords did not appear for those papers)
```{r}
colnames(df)[colSums(is.na(df)) > 0]
```

```{r}
df$pagecount=replace_na(df$pagecount, 1)
```

```{r}
df[is.na(df)] = 0
```


```{r}
glimpse(df)
```

Train/dev/test/split 

```{r}
df_train<-filter(df, split==0)
df_dev<-filter(df,split==1)
```


#Logistic Regression  with LASSO penalization with cv.glmnet 

```{r}
library(glmnet)
```
Model - takes some time to fit - maybe 10 minutes on my machine 
```{r}
set.seed(1)
model<-model.matrix(~ ., data=select(df_train, -tc, -tcB, -pagecount, -split)) #don't forget to remove variables you don't want to regress on 
fit=cv.glmnet(x=model, y=df_train$tcB, alpha=1, family='binomial')
plot(fit)

```
See what the best lambda is and what are the important variables 
```{r}
bestlam=fit$lambda.min
bestlam
coef(glmnet(model, df_train$tcB, alpha=1, lambda=bestlam))
```
```{r}
testpred=predict(fit, newx = model.matrix(tcB ~ . -pagecount -tc -split, data=df_dev), s=bestlam, type="response")

```

# Make Plots 
```{r}
library(pROC)
```

```{r}
ROC1 <- roc(df_dev$tcB, testpred, ci=TRUE, ci.alpha=0.95, plot=TRUE, print.auc=TRUE, legacy.axes=TRUE)
sens.ci <- ci.se(ROC1)
plot(sens.ci, type="shape", col="lightblue")
```


```{r}
AUC1 <- auc(ROC1)
AUC1
```
```{r}
library(precrec)
```
```{r}
precrec_obj <- evalmod(scores = testpred, labels = df_dev$tcB)
autoplot(precrec_obj) 
```
